\documentclass[12pt,letterpaper,oneside,english]{book}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\usepackage{babel}

\usepackage{palatino}
\linespread{1.05}

\begin{document}

\title{The Summer Story}


\author{Adam Lloyd}

\maketitle
\tableofcontents{}


\chapter{A Bright Nightfall}

``That,'' said Will's sister, ``is a lamp.''

``Uh-huh,'' Will confirmed.

She paused. ``And it's \emph{working}.''

``Uh-huh.''

``Well when did that happen? Last I checked, we couldn't \emph{have}
power.''

Their mother broke in. ``We have power because your father has
been working on it for the past three years. Be respectful for once,
Susan.''

``Everything okay?'' The deep male voice was muffled by the distance,
but the three could still discern both the hope and the fatigue within
it.

``It's perfect, honey!'' Will's mother replied. ``Come up and
rest awhile, and enjoy the light.''

A moment later, her husband appeared in the corner of the room from
his basement workshop. He was a middle-aged man of medium height and
a strong build, and at the moment he looked just as weary as he sounded.
His shaggy hair was a mess, and he wiped a bead of sweat from his
brow as he walked into the room. Nonetheless, he wore a triumphant
grin.

``Did it!'' he exclaimed. Before he could enjoy the moment sufficiently,
however, he was interrupted by a loud \emph{pop} from the direction of
the lamp, and he and his family were left in darkness.

Silence.

``Well,'' offered Will's mother, ``\emph{almost} perfect.''

Susan laughed, and to the relief of all present, so did her father.
``Simple enough to fix,'' he said. ``Just a matter of reducing the
output. Well, that and replacing the bulb.'' He chuckled again, and the
rest of the family joined in the laughter. ``I'll be right back,'' he
said.

``And I'll get to work on that light bulb,'' his wife added.  The two
left the room.

Though her brother couldn't make it out in the sudden darkness, Susan's
playful expression turned to one of seriousness. ``So what do you
think?'' she asked.

Will shrugged as their eyes adjusted to the dim light from the windows.
I don't know,'' he answered. ``But I think I'll miss doing everything by
moonlight.''

\medskip
{\centering\rule{\linewidth}{1pt}}
\smallskip

``So explain to me again,'' Will asked, the following day, ``why
we weren't allowed to have electricity.''

His father, who had just resurfaced from his workshop, sighed heavily
and walked to a chest in the corner of the room. He opened a drawer
and, a moment later, handed Will a thin envelope. ``Read it for
yourself,'' he said, then turned and left.

Will stared at it. There was no delivery address, but he could make out
a few faded gold letters where the return address would have been. The
first line read \textsc{Utopia}---a city, and one with which Will was
vaguely familiar in the same way that anyone today is familiar with New
York City or Tokyo. The next line, though present, was too small and
faded for Will to make out.

He opened the envelope and retrieved the single sheet inside. It was
heavy letter paper, watermarked with a symbol Will assumed to be
Utopia's emblem. What had appeared in gilded letters as a return address
on the envelope was reproduced on the letterhead: \textsc{Utopia -
Department of Resource Management}.  A short notice followed; Will began
to read:

\medskip
\framebox{
\begin{minipage}{0.8\linewidth}
\textsc{To whom it may concern:}\\

Be advised that as of January 27, 2206, all power will be routed
directly to Utopia in order to support maintenance and upkeep of our
city as well as our research and development efforts. Any power
generation plant failing to comply with this policy will be immediately
seized. All concerns should be directed to the Department of Outside
Complaints, where they will be dealt with as seen fit.\\

Thank you.
\end{minipage}
}
\medskip

He turned to face his mother, who was at the stove, busily preparing
lunch. ``And did no one ever write to the Department of Outside
Complaints?''

``Of course they did,'' she replied. ``The entire village wrote to them,
and I'm sure it was no different anywhere else.''

``And?''

``And no one ever got a reply. Our electricity was shut off the next
day, and it never came back on, despite the dozens of letters we mailed
out.''

Will seemed taken aback by this. ``The \emph{next day}?'' he repeated.

``Oh, yes,'' his mother replied, ``the next day. They delivered the
notices on the day before the shut-off date.''

Will's father, reappearing, grunted in agreement.  ``Two men in suits in
a black car. Brought out those letters and just tossed them on the
ground in the village center. Drove off again before we could read them,
of course.'' He chuckled nastily. ``Probably knew they wouldn't get
away, otherwise.''

Sensing the anger in her husband's voice, Will's mother cut him off.
``How's it going, dear? Are you about ready for lunch?''

He sighed. ``Yeah, I think I'm done for now. I just have a little more
work to do later, and I should be ready to test it tonight.''

``Okay,'' Will's mother said, looking pointedly at her son before
turning back to the stove.

Will took the hint and folded the letter and returned it to its
envelope before asking the next pressing question. ``Test it?''

His father nodded. ``Yes, test it. I'll be connecting it to the town
power lines tonight.''

``What if something goes wrong?''

He sighed wearily. ``I wouldn't do it if I weren't confident that
nothing will go wrong. Still, if there \emph{is} a problem, the worst it
will do is leave us without power.''

Will nodded. ``Point taken. Does everyone already know you're doing it?''

His father hesitated. ``Well\ldots{}no.''

Will gaped. ``You haven't told \emph{anyone}?''

``Not exactly,'' he replied, ``Paul knows.''

``Oh.''

For as long as Will could remember, Paul had been a good friend of the
family and a best friend of Will's father. He had also somehow earned
the complete trust of the townspeople when the power was shut off, so
Will knew it was okay that he alone had knowledge of the test. If
anything, Paul had probably requested that no one be told about it---as
much faith as he had in Will's father, he undoubtedly knew how cruel it
would be to get the villagers' hopes up before the system was proven
ready.

Satisfied, Will moved along in his list of questions. ``And it will be
able to power the whole town?''

``Based on the testing I've done so far, yes. Of course, I don't know
the exact requirements of the town or how much the system can scale, but
I think it should be more than strong enough. I won't know for sure
until tonight, but I'm confident.''

Next question. ``How long will it last?''

``I'm not sure how much this will change when it's serving the whole
town, but it uses resources very slowly. Given that it runs on weeds and
the unused bits of fruits and vegetables, it's very renewable, as
well.''

Will nodded and opened his mouth to continue, but his mother stopped
him. ``Will,'' she said, ``stop pestering your father and go find
Susan. Lunch is ready.''

Reluctantly, he shut his mouth and left to locate his sister.

\medskip
{\centering\rule{\linewidth}{1pt}}
\smallskip

Will made his way slowly through the cornfield, his eyes peeled for a
sign of his sister's dark hair among the stalks. He knew that this was
one of her usual hangouts, but could never figure out why. It was
private and quiet, certainly, but Will had never thought his sister the
`private and quiet' type.

\textit{She'd make a good scarecrow, maybe.} He chuckled to himself.
Unfortunately, he was so distracted by his own joke that he failed to
notice the slender column of green bent sideways at his feet. His next
step hooked him neatly underneath the stalk and sent him tumbling
forward into the space between the next two rows of corn. He had just
time to right himself before having his attention drawn, by a deafening
shriek, to the two entwined bodies inches from where he had landed.

Will's eyes bugged. ``S-Sis!'' he yelled, half in shock and half in
disbelief. ``And,'' he paused, then his eyes bugged even more.
``\emph{Grant MacCorrin?}''

His jaw would have dropped, had his sister not already freed herself
from her companion's grasp and pinned him to the ground by the time he
had gotten the name out of his mouth. ``Will,'' she began, with more
threat in her tone than her brother had thought she could muster over a
lifetime, ``you tell \emph{anyone} about this, and I'll make sure you
never have \emph{any} use for a girlfriend of your own.'' Will managed
the best nod he could---given that he was pinned by the throat---and his
sister released him and turned back to the boy behind her. 

``Granty, I'm sorry,'' she said. ``Don't worry; he knows better than to
open that little mouth of his.'' Will watched him nod hastily, looking
probably as terrified as Will himself had looked a moment earlier.
\textit{Poor guy,} he thought, \textit{I'd be scared to death, too, if I
were him right about now.} Of course, Will didn't know what Grant was
more frightened by at that point: the thought of what Susan's parents
might do to him if they knew he was courting their daughter, or the fact
that he had just seen someone about his size grounded by the girl whose
lips he had been attached to a moment before.

Grant MacCorrin was, put simply, the village fool. He was 21, five years
older than Will and three older than Susan, but he had never held a job or
made anything productive of himself. He was too weak to work on a farm
and, although he was more intelligent than most, he had nearly flunked out
of school and had no respect among the villagers. The word was that even
his own family only put up with him because they knew he wouldn't make it
on his own.

Grant's status aside, it was no secret that Susan's parents wanted her
to end up with Jed Fellows. Jed was the youngest of three siblings, and
his elder brothers had already started families and successful farms of
their own. Rumor had it that Jed would make more of a name for himself
then even his brothers and that he was interested in having Susan by his
side as he did it. 

Will coughed and turned away. ``When you've fixed yourself up,'' he said
as a blushing Susan pulled her shirt back down to her waist, ``I'm
supposed to be taking you in for lunch. Mom sent me.''

After directing a dirty look at her brother, Susan turned to the still
trembling Grant and, figuring the damage was already done, kissed his
cheek. ``Later, Granty,'' she said, and turned to follow her brother
inside.

\medskip
{\centering\rule{\linewidth}{1pt}}
\smallskip

An unsurprisingly silent walk found Will and his sister in the dining room
in the middle of a serious discussion between their father and Paul.

``And what if,'' Paul asked, ``they see it as a power generation plant and
try to seize it?''

``They won't,'' Will's father replied. ``They disconnected the main
power lines from our town lines long ago. If I'm correct---and I'm
confident that I am---our town is an isolated unit and well off their
radar.''

Sensing some doubt still in Paul's expression, he continued. ``Besides, I
hardly see how some little thing in a farmer's basement could qualify as a
`power generation plant'. It's way too small-scale for that.''

Paul nodded. ``Fine. It runs on junk, anyway, right? If they want to seize
control then they'll have to send someone down here to keep the thing
running. They can't make us do that.'' Sighing, he rose from the table.
``Well, that's it, then. Seven o'clock tonight, right, Tom?''

``That's right.''

``And you're really that sure that this thing will work. I don't want
everyone's world to light up for a minute only so I can tell them once
again that they can't have it.''

``I know, Paul. And I am confident. We'll have light again. You don't need
to worry.''

``Alright,'' Paul replied, his voice still obviously laden with worry.
He turned toward the door. ``Sorry to keep you kids from your lunch.''
He winked at Will and Susan, then left.

``Seven o'clock, daddy?'' Susan asked the second he was out of sight.
``What's seven o'clock?''

``He's testing the power on the town,'' Will answered for him.

``Oh, that's great!'' She glanced at the old grandfather clock in the
corner. ``Then just five more hours until this place lights up again!''

``Let's hope,'' her father replied. ``Let's hope.''

\medskip
{\centering\rule{\linewidth}{1pt}}
\smallskip

At the edge of Will's family's farm, the land rose a bit, forming a sort
of hill that overlooked almost the entire farm and from which one could
see almost directly into the town center. This was where Will stood that
night in the twilight, waiting for his father's test to begin. Like
Susan, he had slipped out unnoticed from the panicky workshop that his
entire house had become that afternoon.

On a normal day---like any other day he could remember---on a warm evening
like tonight he would sit on the hill at the foot of a large maple tree
and watch twilight and then darkness descend over the fields and the town.
Tonight, however, was different. Will realized that this could well be the
last nightfall he watched without the blaze of lights from the town in the
distance.

So he watched. He watched as individual corn stalks became
indistinguishable in the darkness. He watched as a few deep blue and
purple clouds settled into a cool, nightly gray on the horizon. And as
the details in the distance began to vanish, he looked above him to
watch the stars begin to appear. He watched a twinkle appear here and
there, at first scattered about the sky, until the entire milky way
was shining brightly.

\textit{It's beautiful,} he thought. \textit{It's like an ocean.} His gaze
traveled back to the clouds on the horizon. \textit{And those are like
islands. Or like dunes in the sand.} He continued to stare in awe toward
the heavens until his thoughts were interrupted by a sudden streak of
white. \textit{A shooting star!} He closed his eyes. \textit{A wish,} he
thought. \textit{I should make a wish. But for what?} He paused for a
moment, in thought. \textit{I wish,} he began at last, \textit{that one
day I could know what it feels like to be up there.} He closed his eyes
harder for a moment, as if to make sure the wish got through, then,
hastily, added \textit{and I wish that my father's test is successful.}

With that, he opened his eyes. He could see a few of the streets in the
town and a few details of buildings. He could see a light from the window
of his house across the fields, and a few more windows in the town were
beginning to light up. Will had no doubt that people had long since
unplugged and packed away their lamps, seeing no use for them or even
regarding them as cruel reminders of their powerlessness---in more ways
than one. That light was shining from even a few windows meant that the
test was a success.

Will smiled. He was certainly accustomed to the world without electricity,
but whether it felt uncomfortable to him or not, he knew how much it meant
to the townspeople and he was happy for his father. \textit{And,} he
thought, \textit{at least one of my wishes came true.}


\chapter{} %TODO

``I am extremely humbled,'' he began, ``to be speaking before you
tonight.''

``Not only do I stand before the brightest, most talented, and most
powerful men and women in the world, I stand on the shoulders of giants.

``Five generations of giants have worked to bring us here. I think, if
you'll pardon my centuries-old clich\'e, that we can \emph{all} see a
little farther by standing on their shoulders.''

With a dramatic wave of the speaker's arm, the room's lights dimmed and
the ceiling and walls vanished. He chuckled to himself as he waited for
the hundreds of awed murmurs and moans to begin dying away. Most
powerful people in the world or not, he knew that few in his audience
had yet beheld the view from the top of the government building.

He couldn't have wished for a better place for his little show. The
government tower stood, the tallest building in the city, at the precise
center of the dome. His audience would spend nearly a minute looking
in every direction onto the rooves of hundreds of white skyscrapers
around them.

Then they'd move onto the landscape beyond. The base of the city's dome
stood nearly a mile above the ground, and if you ventured to an edge on
a clear day, you'd be greeted with a fantastic view. From the government
building's banquet hall, you could see as far as you liked in any
direction---you just had to decide which way to turn.

It was a difficult choice, the speaker knew, so he had offered his
audience a little help. He watched as the collective gaze moved from the
mountains in the north to the ocean in the east and then to the river
that flowed south past the city, all subtly lit by satellite. And then,
finally, he gave a nudge to the brightness of the sky and watched the
room's attention turn upward.

He was proud of this part; he had prepared a spectacular bowl of stars
for the event, and he was pleased to hear a sharp crescendo in his
audience's gasps. None of them had seen the Milky Way shine in such
glory---partly, he figured, because it never really had.

``Two hundred years ago,'' he continued when the noise had died down,
``this scientific paradise did not exist. But there were seeds.''

He gestured to his right, and sky behind him was replaced with a
late twentieth-century cityscape. ``Two hundred years ago, three great
men lived here. They grew up like everyone around them: in fear of
disease. Cancer. AIDS. One of the men had a close call with meningitis;
another was diabetic.

``Today, we barely know what those names mean. Those men had the seeds
of our great society. Seeds so tiny that they were imperceptible to the
human eye, but seeds so great that they were able to eradicate disease.

``Scientists---my great great grandfather among them---came by the dozen
to have a hand in the furthering of this fantastic nanotechnology.
Others came, too: artists, writers, great politicians---people like
yourselves came to live in what quickly became known as the great land
of healing.''

As he talked, the city on his right had been slowly expanding. The
skyscrapers had nearly doubled in number, and many densely populated
suburbs had sprung up. Now, the scene darkened.

``And then World War III began. In a day, the face of the world was
changed. Countless cities---including Washington, our nation's former
capital---were leveled in the opening shots of nuclear weaponry. But
then the blows came in the form of something much worse for that time:
biological warfare.

``People flocked to our sickness-free paradise, and by virtue of the
tiny healing chips our forefathers invented, the city outlasted every
other warring nation.''

Beside him, the scene cast off the grim reddish tint of war. It became
dominated instead by a thick cylindrical platform rising hundreds of
feet above the center of the old city.

``It was a prosperous time,'' he continued, ``and the new capital
was built in all the glory it deserved---right on top of the home of
the country's savior.''

\end{document}
