\documentclass[12pt,letterpaper,oneside,english]{book}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\usepackage{babel}

\usepackage{palatino}
\linespread{1.05}

\begin{document}

\title{The Summer Story}


\author{Adam Lloyd}

\maketitle
\tableofcontents{}


\chapter{A Bright Nightfall}

``That,'' said Will's sister, ``is a lamp.''

``Uh-huh,'' Will confirmed.

She paused. ``And it's working.''

``Uh-huh.''

``Well when did that happen? Last I checked, we couldn't \emph{have}
power.''

Their mother broke in. ``We have power because your father has
been working on it for the past three years. Be respectful for once,
Susan.''

``Everything okay?'' The deep male voice was greatly muffled by
the distance, but the three could easily pick up both the hope and
the fatigue within it.

``It's perfect, honey!'' Will's mother replied. ``Come up and
rest a while, and enjoy the light.''

A moment later, her husband appeared in the corner of the room from
his basement workshop. He was a middle-aged man of medium height and
a strong build, and at the moment he looked just as weary as he sounded.
His shaggy hair was a mess, and he wiped a bead of sweat from his
brow as he walked into the room. Nevertheless, he wore a triumphant
grin.

``Did it!'' he cried. Before he could enjoy the moment sufficiently,
however, he was interrupted by a loud \emph{pop} from the direction
of the lamp, and he and his family were left in darkness.

Silence.

``Well,'' offered Will's mother, ``\emph{almost} perfect.''

Susan laughed, and much to the relief of all present, her father joined
in. ``Simple enough to fix,'' he said. ``Just a matter of reducing
the output. Well, that and replacing the bulb.'' He chuckled again,
and the rest of the family joined in the laughter. ``I'll be right
back,'' he said.

``And I'll get to work on that light bulb,'' his wife replied.
The two left the room.

Though her brother couldn't make it out in the sudden darkness, Susan's
playful expression turned to one of seriousness. ``So what do you
think?'' she asked.

Will shrugged as their eyes adjusted to the dim light coming through
the many windows. I don't know,'' he answered. ``But I think I'll
miss doing everything by moonlight.''

\medskip
{\centering\rule{\linewidth}{1pt}}
\smallskip

``So explain to me again,'' Will asked, the following day, ``why
we weren't allowed to have electricity.''

His father, who had just resurfaced from his basement workshop, sighed
heavily and walked over to a chest in the corner of the room. He opened
a drawer and, a moment later, handed Will an thin envelope. ``Read
it for yourself,'' he said, then turned and left.

Will stared at the envelope for a moment. There was no delivery address,
but he could make out a few faded gold letters where the return address
would have been. The first line read \textsc{Utopia}---a city, and one
with which Will was vaguely familiar in the same way as anyone today
is familiar with New York City or Tokyo. The next line, though present,
was too small and faded for Will to make out.

He opened the envelope and retrieved the single sheet of letter paper
inside. It was heavy paper, watermarked with a symbol Will had never
before seen but assumed to be Utopia's emblem. What had appeared in
gilded letters as a return address on the envelope was reproduced
on the letterhead: \textsc{Utopia - Department of Resource Management}.
A short notice followed; Will began to read:

\medskip
\framebox{
\begin{minipage}{0.8\linewidth}
\textsc{To whom it may concern:}\\

Be advised that as of January 27, 2106, all power will be routed
directly to Utopia in order to support maintenance and upkeep of our
city as well as our research and development efforts. Any power
generation plant failing to comply with this policy will be immediately
seized. All concerns should be directed to the Department of Outside
Complaints, where they will be dealt with as seen fit.\\

Thank you.
\end{minipage}
}
\medskip

He turned to face his mother, who was at the stove, busily preparing
lunch. ``And did no one ever write to the Department of Outside
Complaints?''

``Of course they did,'' she replied. ``The entire village wrote to them,
and I'm sure it was no different anywhere else.''

``And?''

``And no one ever got a reply. Our electricity was shut off the next
day, and it never came back on, despite the dozens of letters we mailed
out.''

Will seemed taken aback by this. ``The \emph{next day}?'' he repeated.

``Oh, yes,'' his mother replied, ``the next day. They delivered the
notices on the day before the shut-off date.''

Will's father, who had just reappeared, grunted in agreement.
``Two men in suits in a black car. Brought out those letters and just
tossed them on the ground in the village center. Drove off again before
we could read them, of course.'' He chuckled nastily. ``Probably knew
they wouldn't get away, otherwise.''

Sensing the growing anger in her husband's voice, Will's mother cut him
off. ``How's it going, dear? Are you about ready for lunch?''

He sighed. ``Yeah, I think I'm done for now. I just have a little more
work to do later, and I should be ready to test it tonight.''

``Okay,'' Will's mother said, looking pointedly at her son before
turning back to the stove.

Will took the hint and folded the letter and returned it to its
envelope before asking the next pressing question. ``Test it?'' he
questioned.

His father nodded. ``Yes, test it. I'll be connecting it to the town
power lines tonight.''

``What if something goes wrong?''

He sighed wearily. ``I wouldn't do it if I weren't confident that
nothing will go wrong. Still, if anything does go wrong, probably the
worst it will do is leave us without power.''

Will nodded. ``Point taken. Does everyone already know you're doing it?''

His father hesitated. ``Well\ldots{}no.''

Will seemed shocked. ``You haven't told \emph{anyone}?''

``Not exactly,'' he replied, ``Paul knows.''

``Oh.''

Paul had been a good friend of the family and a best friend of his
father for as long as Will could remember. It was no surprise that he
knew of the testing, and his position as the town mayor made it okay
that he was the only one who knew. Having not been old enough to
remember when the power was shut off, Will did not know why the
townspeople trusted Paul so completely, but he knew that they did. If
Paul knew about the testing and was permitting it, then it was not
worrisome that no one else knew yet. If anything, Paul had probably
requested that no one be told until the system was up and running
properly. As much faith as he had in Will's father, Paul undoubtedly
knew that it would be cruel to get the townspeople's hopes up for
nothing.

Satisfied, Will moved along in his list of questions. ``And it will be
able to power the whole town?''

``Based on the testing I've done so far, yes. Of course, I don't know
the exact requirements of the town or how much the system can scale, but
I think it should be more than strong enough. I won't know for sure
until tonight, but I'm confident.''

Next question. ``How long will it last?''

``I'm not sure how much powering the whole town will change this, but it
uses resources very slowly. Given that it runs on weeds and the unused
bits of fruits and vegetables, it is very renewable, as well.''

Will nodded and opened his mouth to continue, but his mother stopped
him. ``Will,'' she said, ``stop pestering your father and go find
Susan. Lunch is ready.''

Reluctantly, he shut his mouth and went outside to locate his sister.

\medskip
{\centering\rule{\linewidth}{1pt}}
\smallskip

Will made his way slowly through the corn field, his eyes peeled for a
sign of his sister's dark hair among the stalks. He knew that the corn
field was one of her usual hangouts, but could never figure out why. It
was private and quiet, certainly, but Will had never thought his sister
the `private and quiet' type.

\textit{She'd make a good scarecrow, maybe.} He chuckled to himself.
Unfortunately, he was so distracted by his own joke that he failed to
notice the slender column of green bent sideways at his feet. His next
step hooked him neatly underneath the stalk and sent him tumbling forward
into the space between the next two rows of corn. He had just time to
right himself before having his attention drawn, by a nearly deafening
shriek, to the two entwined bodies inches from where he had landed.

Will's eyes bugged. ``S-Sis!'' he yelled, half in shock and half in
disbelief. ``And,'' he paused, then his eyes bugged even more.
``\emph{Grant MacCorrin?}''

His jaw would have dropped, had his sister not already freed herself from
her companion's grasp and pinned him to the ground of the corn field by
the time he had gotten the name out of his mouth. ``Will,'' she began,
with more threat in her tone than her brother had ever thought she could
muster over a lifetime, ``you tell \emph{anyone} about this, and I'll make
sure you never have \emph{any} use for a girlfriend of your own.'' Will
managed the best nod he could, given that he was pinned by the throat, and
his sister released him and turned back to the young man behind her. 

``Granty, I'm sorry,'' she said. ``Don't worry; he knows better than to
open that little mouth of his.'' Will watched him nod hastily, looking
probably as terrified as Will himself had looked just a moment earlier.
\textit{Poor guy,} he thought, \textit{I'd be scared to death, too, if I
were him right about now.} Of course, Will didn't know what Grant was more
frightened of at that point: the thought of what Susan's parents might do
to him if they found out, or the fact that he had just seen someone about
his size grounded by the girl whose lips he had been attached to not long
before.

Grant MacCorrin was, put simply, the village fool. He was 21, five years
older than Will and three older than Susan, but he had never held a job or
made anything productive of himself. He was too weak to work on a farm
and, although he was more intelligent than most, he had nearly flunked out
of school and had no respect among the villagers. The word was that even
his own family only put up with him because they knew he wouldn't make it
on his own.

Grant's status aside, it was no secret that Susan's parents wanted her to
end up with Jed Fellows, the youngest of the three Fellows boys. His two
older brothers had already started farms and families of their own and
were highly successful and respected. Rumor had it that Jed would make
more of a name for himself then even his brothers and that he was
interested in having Susan by his side as he did it. 

Will coughed and turned away. ``When you've fixed yourself up,'' he said
as a blushing Susan pulled her shirt back down to her waist, ``I'm
supposed to be taking you in for lunch. Mom sent me.''

After directing a dirty look at her brother, Susan turned to the still
trembling Grant and, figuring the damage was already done, kissed his
cheek. ``Later, Granty,'' she said, and turned to follow her brother
inside.

\medskip
{\centering\rule{\linewidth}{1pt}}
\smallskip

An unsurprisingly silent walk found Will and his sister in the dining room
in the middle of a serious discussion between their father and Paul.

``And what if,'' Paul asked, ``they see it as a power generation plant and
try to seize it?''

``They won't,'' Will's father replied. ``They disconnected the main power
lines from our town lines long ago. If I'm correct, and I'm confident that
I am, our town is an isolated unit and well off their radar.''

Sensing some doubt still in Paul's expression, he continued. ``Besides, I
hardly see how some little thing in a farmer's basement could qualify as a
`power generation plant'. It's way too small-scale for that.''

Paul nodded. ``Fine. It runs on junk, anyway, right? If they want to seize
control then they'll have to send someone down here to keep the thing
running. They can't make us do that.'' Sighing, he rose from the table.
``Well, that's it, then. Seven o'clock tonight, right, Tom?''

``That's right.''

``And you're really that confident that this thing will work. I don't want
everyone's world to light up for a minute only so I can tell them once
again that they can't have it.''

``I know, Paul. And I am confident. We'll have light again. You don't need
to worry.''

``Alright,'' Paul replied, his voice still obviously laden with some
worry. He turned toward the door. ``Sorry to keep you kids from your
lunch.'' He winked at Will and Susan, then left.

``Seven o'clock, daddy?'' Susan asked the second he was out of sight.
``What's seven o'clock?''

``He's testing the power on the town,'' Will answered for him.

``Oh, that's great!'' She glanced at the old grandfather clock in the
corner. ``Only five more hours until this place lights up again!''

``Let's hope,'' her father replied. ``Let's hope.''

\medskip
{\centering\rule{\linewidth}{1pt}}
\smallskip

At the edge of Will's family's farm, the land rose a bit, forming a sort
of hill that overlooked almost the entire farm and from which one could
see almost directly into the town center. This was where Will stood that
night in the twilight, waiting for his father's test to begin. Like Susan,
he had slipped out unnoticed from the panicky workshop that his house had
become that afternoon.

On a normal day, like any other day he could remember, on a warm evening
like tonight he would sit on the hill at the foot of a large maple tree
and watch twilight and then darkness descend over the fields and the town.
Tonight, however, was different. Will realized that this could well be the
last nightfall he watched without the blaze of lights from the town in the
distance.

So he watched. He watched as the individual corn stalks became
indistinguishable in the darkness. He watched as a few deep blue and
purple clouds settled into a cool, nightly gray on the horizon. As the
details in the distance began to vanish, he looked above him to watch the
stars start to appear. He watched a twinkle appear here and there, at
first scattered about the sky, and soon the entire milky way was shining
brightly.

\textit{It's beautiful,} he thought. \textit{It's like an ocean.} His gaze
traveled back to the clouds on the horizon. \textit{And those are like
islands. Or like dunes in the sand.} He continued to stare in awe toward
the heavens until his thoughts were interrupted by a sudden streak of
white. \textit{A shooting star!} He closed his eyes. \textit{A wish,} he
thought. \textit{I should make a wish. But for what?} He paused for a
moment, in thought. \textit{I wish,} he began at last, \textit{that one
day I could know what it feels like to be up there.} He closed his eyes
harder for a moment, as if to make sure the wish got through, then,
hastily, added \textit{and I wish that my father's test is successful.}

With that, he opened his eyes. He could see a few of the streets in the
town and a few details of buildings. He could see a light from the window
of his house across the fields, and a few more windows in the town were
beginning to light up. Will had no doubt that people had long since
unplugged and packed away their lamps, seeing no use for them or even
regarding them as cruel reminders of their powerlessness, in more ways
than one. That light was shining from even a few windows meant that the
test was a success.

Will smiled. He was certainly accustomed to the world without electricity,
but whether it felt uncomfortable to him or not, he knew how much it meant
to the townspeople and he was happy for his father. \textit{And,} he
thought, \textit{at least one of my wishes came true.}


\chapter{} %TODO

Utopia was not the sort of thing usually called to mind when thinking of
'cities'.  In one respect, this was fairly obvious: the traditional city
doesn't sit atop Utopia's massive white tower.  The traditional city
also doesn't loom in the sky, its symbolic white dome a sickening
reminder to everyone within miles of their place in the world.

Utopia was not the traditional city.  But it \emph{was} the only one,
and certainly the only one that mattered.  Indeed, to the residents of
Utopia, there was nothing else.  The redirection of the world's power
was one of the few instances in which---unpleasantly---any Utopians were
forced to consider the outside world.

It had started slowly.  At first---well before the days of the current
Utopia---people just thought it was a great place to live.  A few
influential scientists moved in, and Utopia gradually gathered a
reputation for housing the state of the art in nearly every imaginable
field.  This drew in more people and more researchers, and the pace of
development quickened.

Like a forming star, the city kept pulling in more and more people and
talent, faster and faster.  Utopia eventually gained enough power in the
national government that it was able to uproot and consume it entirely.

Building the new capital gave Utopia's leaders a chance to scratch a few
other itches.  As it amassed its population, the city had been forced to
stretch its borders---a little too far, some thought.  It had also
gained a significant number of the sort of people that the powerful
visionaries saw as undesirable.

As the crime rate rose, so did the core of Utopia.  The massive new
capital was built directly atop what had been the center of the old
city.  All of the scientists and great thinkers that had brought the
city's success were simply shifted a few hundred feet toward the sky
with it.

The core had not physically isolated itself from its
surroundings---plenty of grand, looping highways were built to climb
their way to its height---but symbolically, it certainly had.

This became a pattern for city: seize a little power, get a little
bigger, come upon a few issues, and then pave the streets of its next
incarnation right on top of them.

After the new capital was completed, Utopia set its sights on a larger
domain.  While it made it clear that it felt little for the people of
the outside world, it acknowledged that the outside world had plenty of
useful resources.

What the outside world \emph{didn't} have was the advanced weaponry and
military genius centered in Utopia.  Country after country fell quickly,
with few even putting up a fight.  Operations that Utopia's leaders
deemed useful were left running, and the people that Utopia's leaders
deemed useful were brought to Utopia; everything else was decimated.

% TODO: come upon a few issues?  I think this is really going downhill
% here.

With near-infinite resources and no outside threats, Utopia set about
its second great rebuilding.  The tower of the former ``new capital''
served as a base for Utopia's new half-sphere in the sky.

\medskip
{\centering\rule{\linewidth}{1pt}}
\smallskip

Power wasn't one of the resources that Utopia initially seized.  For a
while, it was able to keep itself running.  When the third
rebuilding---the top of the now-familiar Utopian dome---began, however,
it became apparent that self-sufficiency was no longer possible.  The
planned tall, white, and entirely computerized skyscrapers would simply
require too much energy.

The Department of Resource Management had just moved into its own tall,
white tower when it made the decision.  A few nights later, those in
charge watched one of the large, wall-sized computer screens as their
satellites saw the entire planet---except for the one brilliant spot
representing Utopia---go dark.

One night many years later, Utopia's newly appointed chief scientist sat
looking with pride at that very same singular brilliant spot through the
eyes of these very same satellites.  He was more than a little surprised
when a second point on the map lit up.

\end{document}
